### 2024-01-04 tesis_Ashish/Chapter2/chapter2.tex
Updated thesis 4 Jan 2024

\item Hadron Forward Calorimeter: The Hadron Forward (HF) Calorimeter is a critical component of the CMS experiment. It is a subdetector that measures the energy, position and arrival time of particles produced during proton-proton collisions. The HF Calorimeter is designed specifically to measure hadron particles, which are particles made up of quarks and gluons, in the forward region (i.e., close to the beamline) of the CMS detector. The HF Calorimeter is located at the very front and back of the CMS detector, at a distance of about 11.2 meters from the interaction point. This placement allows it to cover a pseudorapidity range of 2.9 to 5.2, which is important for measuring particles produced at small angles relative to the beamline. The HF Calorimeter is a sampling calorimeter, which means it consists of alternating layers of active and passive materials. The active material, in this case, is scintillating quartz fibers, which emit light when they interact with charged particles. The passive material is steel absorber plates, which serve to initiate hadron showers, causing the incident hadron to interact and create secondary particles. As these secondary particles pass through the scintillating fibers, they produce light, which is collected by photodetectors and converted into an electrical signal proportional to the particle's energy. Two separate algorithm are used for luminosity measurement in the HF Calorimeter, HFOC and HFET based on the Zero Counting (ZC) method and the Missing Transverse Energy (MET) methods respectively \cite{CMS-PAS-LUM-15-001}.

@@

The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively. The PCC method has achieved a relative luminosity precision of about 1.5 \%, which is well within the design goals of the CMS \cite{CMS-PAS-LUM-18-002}. In the future, the PCC method will continue to be a key component of the CMS luminosity measurement strategy, as it provides a precise and robust measurement of the luminosity ratio between different datasets and periods. The PCC method will also benefit from the upgrades and improvements planned for the CMS pixel detector and the LHC, which will increase the luminosity and the collision rate, and will challenge the performance and the calibration of the PCC method. The CMS is planning to install a new pixel detector for the High-Luminosity LHC (HL-LHC) era, which will feature smaller pixel sizes, faster readout electronics, and radiation-hard materials. The CMS is also planning to develop new techniques and algorithms for the PCC method, such as machine learning methods, deep neural networks, and real-time analysis tools.

>>>>

\item Hadron Forward Calorimeter: The Hadron Forward (HF) Calorimeter is a critical component of the CMS experiment. It is a subdetector that measures the energy, position and arrival time of particles produced during proton-proton collisions. The HF Calorimeter is designed specifically to measure hadron particles, which are particles made up of quarks and gluons, in the forward region (i.e., close to the beamline) of the CMS detector. The HF Calorimeter is located at the very front and back of the CMS detector, at a distance of about 11.2 meters from the interaction point. This placement allows it to cover a pseudorapidity range of 2.9 to 5.2, which is important for measuring particles produced at small angles relative to the beamline. The HF Calorimeter is a sampling calorimeter, which means it consists of alternating layers of active and passive materials. The active material, in this case, is scintillating quartz fibers, which emit light when they interact with charged particles. The passive material is steel absorber plates, which serve to initiate hadron showers, causing the incident hadron to interact and create secondary particles. As these secondary particles pass through the scintillating fibers, they produce light, which is collected by photodetectors and converted into an electrical signal proportional to the particle's energy. Two separate algorithm are used for luminosity measurement in the HF Calorimeter, HFOC and HFET based on the Zero Counting (ZC) method and the Missing Transverse Energy (MET) methods respectively. %\cite{CMS-PAS-LUM-15-001}.

@@

The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively. The PCC method has achieved a relative luminosity precision of about 1.5 \%, which is well within the design goals of the CMS \cite{pas_18}. In the future, the PCC method will continue to be a key component of the CMS luminosity measurement strategy, as it provides a precise and robust measurement of the luminosity ratio between different datasets and periods. The PCC method will also benefit from the upgrades and improvements planned for the CMS pixel detector and the LHC, which will increase the luminosity and the collision rate, and will challenge the performance and the calibration of the PCC method. The CMS is planning to install a new pixel detector for the High-Luminosity LHC (HL-LHC) era, which will feature smaller pixel sizes, faster readout electronics, and radiation-hard materials. The CMS is also planning to develop new techniques and algorithms for the PCC method, such as machine learning methods, deep neural networks, and real-time analysis tools.
